\chapter*{Acknowledgment\markboth{Acknowledgment}{Acknowledgment}}
Thanking is the best way to appreciate myself for performing a great task. The reason I can claim that I am successful in completing my work with such ease is that the Almighty gave me the ability, capability, chance, cooperating hands, and enough stamina to walk on this path. Almighty enriched me with very good luck on this path of work.
\par The reason I am talking about luck is that I had my respected teacher Prof. Dr. Md. Abdur Razzaque as my supervisor in this work and I would like to take the opportunity to express my sincere gratitude and indebtedness to my respected supervisor. Although he is a self-motivated and hard-working person always loaded with research and administrative works, he gave me more than enough time in this work. I still remember those memorable days, when I returned to my home at around 9 pm. from the department after fruitful discussion with him.
%
\par I am thankful to the MS thesis committee members for their suggestion, corrections and guidelines. It is worth mentioning that, their help and support have influence me reorganize my work, furnish my ideas, find out errors and correcting them. 
%
\par I must aslo be thankful to the ICT department of MoPTIT, GoB, for the fellowship support which has helped me keep full concentration on my thesis work.
%
\par Finally, I would like to thank my mother, my sister and brother-in-law, and my friends for their unconditional love and selfless support.
\begin{flushright}
Tamal Adhikary\\
June 2015
\end{flushright}
